Combinatorics of the geometry of Wilson loop diagrams I: equivalence classes via matroids and polytopes

### 2019-08-10 GWLDCI.tex
removed last comment
first draft abstract and funding thanks

\title{Combinatorics of the geometry of Wilson loop diagrams I: equivalence classes via matroids and polytopes}
\author{Susama Agarwala, Si\^an Fryer, and Karen Yeats}
%\date{}

@@

@@

However, the two approaches are not identical: for example, in the case of Wilson loop diagrams with $k=2$ and $n=6$, past work of Agarwala and Fryer shows that the manifold is not contractible \cite{casestudy}. More generally, it has been shown that the spaces defined by the Amplituhedron and by Wilson loop diagrams are not the same \cite{Amplituhedronsquared}. In fact, it is in some ways more natural to consider Deodhar cells of $\mathbb{G}(k, n+1)$ for Wilson loop diagrams; in this case, one gets that the manifold represented by the diagrams is not orientable \cite{non-orientable}. \note{Check with Cam.}

>>>>

\title{Combinatorics of the geometry of Wilson loop diagrams I: equivalence classes via matroids and polytopes}
\author{Susama Agarwala\thanks{SA was supported by an ONR grant.}, Si\^an Fryer, and Karen Yeats\thanks{KY is supported by an NSERC Discovery grant, by the Canada Research Chair program, and though some the time this work was developed also by a Humboldt Fellowship from the Alexander von Humboldt foundation.}}
%\date{}

@@

\begin{abstract}
  Wilson loop diagrams, an important tool in studying scattering amplitudes, are known by previous work to be associated to positroids.
  We characterize when two Wilson loop diagrams give the same positroid, and enumerate the number of different Wilson loop diagrams that correspond to each positroid cell.  We also give a correspondence between those positroids which can arise from Wilson loop diagrams and directions in associahedra.
\end{abstract}

@@

However, the two approaches are not identical: for example, in the case of Wilson loop diagrams with $k=2$ and $n=6$, past work of Agarwala and Fryer shows that the manifold is not contractible \cite{casestudy}. More generally, it has been shown that the spaces defined by the Amplituhedron and by Wilson loop diagrams are not the same \cite{Amplituhedronsquared}. In fact, it is in some ways more natural to consider Deodhar cells of $\mathbb{G}(k, n+1)$ for Wilson loop diagrams; in this case, one gets that the manifold represented by the diagrams is not orientable \cite{non-orientable}.
